Computer Science House Constitution

### 2017-03-01 articles.tex
swapped an apostrophe for one that actually compiles (#98)

\asection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

>>>>

\asection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
